\section{The Existing System}
{\bf Introduction }\\
Existing system is manual system where there is no role of computer. 
Employees use pen, paper to make records and consignment notes.

{\bf {Limitations of privious system }}
\begin{itemize}
\item There was no use computer.

\item Record keeping was difficult.

\item To search previous notes, they have to search lots of books.

\item It was difficult to track which consignment in dispatched and
which consignment is in waiting stage.

\end{itemize}

\section{Software Functions Provided in Proposed system}

\begin{description}
\item[\bf{Registeration \& Login}:]
The software user would be required to Register through a screen. After 
authentication and login he would be able to access only those areas 
for which he is capable to access.
\item[\bf{Administrator Maintenance}:]
Administrator can add or update the details directly through admin 
interface.
\item[\bf{Consignment Note Generation}:]
The consignment note generation for any consignment is made easier now.
\item[\bf{Consignment Search}:]
Now user can search previous consignment easily and generate consignment 
note if required.
\item[\bf{Dispatch Status}:]
Dispatch Status can be checked easily. 
\end{description}

\section{Introduction to Automation}
Automation is the use of machines, control systems and Information 
Technologies to optimize productivity in the production of goods and 
delivery of services. 

Office automation is intended to provide elements which make it possible to simplify, improve,
and automate the organization of the activities of a company or a group of people.

We show our ingenuity everyday through our associates’ high level of performance. We provide
solutions to help our clients improve internal processes, save money and deliver results. That is
“ingenuity at work”.
Automation is all about using the computer to:
\begin{itemize}
\item Make your work less tedious.
\item Trim hours off your workload.
\item Reduce repetitive keyboard strokes or mouse-clicks.
\item Make data entry easier with fewer tabs or mouse movements.
\item Take any job you do longhand and make the computer do it for you.
\end{itemize}
The use of computer systems to execute a variety of office operations, such as word processing,
accounting, and e-mail refers to what we call automation. Office automation almost always implies
a network of computers with a variety of available programs. Automation helps in optimizing or
automating existing office procedures.

\section{Special Terms Used}
\begin{itemize}
\item Consigner: Person/Organisation who wants to send parcel.
\item Consignee: Person/Organisation to whom parcel is to be sent.
\item Tin: Unique identification number.
\item Freight Mode: Mode of payment.
\item Basic Freight: Minimum Charges.
\item Barrier Charges: Charges regarding road tax.
\item Hamali Charges: Labour charges for loading and unloading.
\end{itemize} 
